---
title: "DATA 607 Spring 2024 - Assignment 3"
author: "Syed Hasan"
output: pdf_document
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(lubridate)
```

#Problem 1 :

```{r, echo=FALSE}
raw_file = 'https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv'
majors <- as_tibble(read.csv(raw_file))
majors_sub <- majors %>% 
    mutate(matched_name = str_match(Major,'.*DATA.*|.*STATISTICS.*')) %>%
    select(Major,matched_name) %>%
    filter(!is.na(matched_name))
majors_sub
```

#Problem 2 : 

```{r, echo=FALSE}
#2 Write code that transforms the data below:
vec.text = c('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"')

vec.text.char = gsub("(\\n\\[\\d+\\])|(^\\[\\d+\\])", "", vec.text)
vec.text.char = strsplit(vec.text.char, '\\"')
vec.text.char = unlist(vec.text.char)
vec.text.char = vec.text.char[grep("[a-z]", vec.text.char)]
print(vec.text.char)
```


#Problem 3 :

(.)\1\1 - Any two characters that repeats in the reverse order.
“(.)(.)\\2\\1” - Any two characters that repeats in the same order.
“(.).\1.\1” - Any single character that repeats two more times, with each repetition after another single variable character.
“(.)(.)(.).*\3\2\1” - Any three characters that repeat in the reverse order after any number of variable characters.

#Problem 4 : 

#Start and end with the same character:
```{r, echo=FALSE}
str_view("eye", "^(.).*\\1$", match = T)
```
#Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r, echo=FALSE}
str_view("church", "(..).*\\1", match = T)
```
```{r, echo=FALSE}
str_view("eleven", "(.).*\\1.*\\1", match = T)
```


