---
title: "Data 607 - Week 5"
author: "Syed Hasan"
date: "2024-02-26"
output: html_document
---


```{r}
library(tidyr)
library(dplyr)
```

```{r}
url <- 'https://raw.githubusercontent.com/SyedHasanMafi/Data-607/main/airlinedata.csv'
airline_data <- read.table(url, header=TRUE, sep=",", na.strings = c("", "NA"))

airline_data
```

```{r}
colnames(airline_data) [1] <- "Airline"
colnames(airline_data) [2] <- "Arrival_Status"

airline_data
```

```{r}
airline_data <- airline_data[rowSums(is.na(airline_data)) != ncol(airline_data), ]

airline_data
```

```{r}
airline_data_long <- gather(airline_data, City, Num_Flights, Los.Angeles:Seattle, factor_key=TRUE)

airline_data_long
```


```{r}
airline_data_long2 <- airline_data_long %>% mutate(Airline = as.character(na_if(Airline, 'NA'))) %>%  fill(Airline, .direction = 'down')

airline_data_long2
```

```{r}
#airline_data_transform %>% spread(airline_data_long2, Arrival_Status, Num_Flights)

airline_data_transform <- airline_data_long2 %>% spread(Arrival_Status, Num_Flights)

#changing name of delayed and on time columns for analysis 

colnames(airline_data_transform) [3] <- "Delayed"
colnames(airline_data_transform) [4] <- "On_Time"

airline_data_transform
```

```{r}
airline_data_transform %>% 
        group_by(Airline) %>% 
        dplyr::summarise(max = max(Delayed),
        min=min(Delayed),
        mean=mean(Delayed),  
        median=median(Delayed),
        standard_deviation=sd(Delayed))
```

Conclusion : 
After thoroughly cleaning and analyzing the data, it is evident that AM WEST performs more poorly than Alaska. This is evident in the higher mean and median delay times, along with greater maximum and minimum delay times for AM WEST. Additionally, the higher standard deviation for AM WEST indicates increased variability in delay times compared to Alaska. Collectively, these observations suggest an overall unfavorable experience for travelers with AM WEST.